Document Expansion with External Collections for Information Retrieval

### 2017-02-09 paper.tex
updated results

@@

\subsection{Is Expansion Worthwhile?}\label{section.results.expansion}

\begin{table}[htbp]
\centering
\begin{tabular}{|l|c|c|c|c|} \hline
& \multicolumn{2}{c}{Self} & \multicolumn{2}{|c|}{Wikipedia} \\ \hline
{\bf Collection} & {\bf $\lambda$} & {\bf MAP} & {\bf $\lambda$} & {\bf MAP} \\ \hline
AP & ? & ? & 0.2 & 0.2662 \\ \hline
Robust & ? & ? & 0.2 & 0.2354 \\ \hline
wt10g & ? & ? & ? & ? \\ \hline
blogs06 & ? & ? & ? & ? \\ \hline
clueweb09 & ? & ? & ? & ? \\ \hline
\end{tabular}
\caption{The top-scoring runs by MAP using only one collection of expansion documents. ``Self'' indicates expansion using the document's original collection while ``Wikipedia'' indicates expansion using Wikipedia.}
\label{table.performance.single}
\end{table}

>>>>

\subsection{Relevance Modeling with Expanded Documents}

While our approach serves much the same role as relevance modeling, the two techniques may in fact be used simultaneously. Practically, the relevance model may be computed on either the unexpanded or the expanded documents. However, there are two reasons why we would prefer the latter case: 
\begin{enumerate}
	\item Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that computing an RM using expanded documents should produce a more accurate relevance model.
	\item Part of the benefit of document expansion is that it may be performed at indexing time, so computing an RM on unexpanded documents ignores information that is already available.
\end{enumerate}

The addition of relevance modeling to our document expansion approach is therefore extremely straightforward: we simply compute the RM as in Eq. \ref{equation.rm1} substituting the expanded document for the original.

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|l|l|l|} \hline
{\bf Collection} & {\bf Exp. Source} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{7}{*}{AP} & \cellcolor{gray!50}{\it Baseline} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2337 & \cellcolor{gray!50}0.4170 \\ \cline{2-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.3310 & \cellcolor{gray!50}0.4855 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Self} & {\it QL} & 0.2694$^\uparrow$ & 0.4519$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Self} & {\it RM3} & 0.3295$^{\uparrow *}$ & \textbf{0.4876}$^{\uparrow *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Wiki} & {\it QL} & 0.2644$^\uparrow$ & 0.4582$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Wiki} & {\it  RM3} & 0.3334$^{\uparrow *}$ & 0.4811$^{\uparrow *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Double} & {\it QL} & 0.2774$^\uparrow$ & 0.4734$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Double} & {\it RM3} & \textbf{0.3342}$^{\uparrow\Uparrow *}$ & 0.4789$^\uparrow$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{7}{*}{Robust} & \cellcolor{gray!50}{\it Baseline} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2183 & \cellcolor{gray!50}0.3867 \\ \cline{2-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.2639 & \cellcolor{gray!50}0.3908 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Self} & {\it QL} & 0.2369$^\uparrow$ & 0.4036$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Self} & {\it RM3} & 0.2591$^{\uparrow\Downarrow *}$ & 0.3894$^{*}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Wiki} & {\it QL} & 0.2326$^\uparrow$ & 0.4040$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Wiki} & {\it RM3} & \textbf{0.2674}$^{\uparrow *}$ & 0.4201$^{\uparrow\Uparrow *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Double} & {\it QL} & 0.2417$^\uparrow$ & 0.4156$^{\uparrow\Uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Double} & {\it RM3} & 0.2672$^{\uparrow *}$ & \textbf{0.4205}$^{\uparrow\Uparrow}$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{7}{*}{wt10g} & \cellcolor{gray!50}{\it Baseline} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.1683 & \cellcolor{gray!50}0.2816 \\ \cline{2-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.1651 & \cellcolor{gray!50}0.2834 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Self} & {\it QL} & 0.1660 & 0.2936 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Self} & {\it RM3} & 0.1694$^\Uparrow$ & 0.2758$^\Downarrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Wiki} & {\it QL} & 0.1780$^\uparrow$ & 0.3029$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Wiki} & {\it RM3} & \textbf{0.2089}$^{\uparrow\Uparrow *}$ & \textbf{0.3085}$^{\uparrow\Uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Double} & {\it QL} & 0.1759 & 0.3148$^{\uparrow\Uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it Double} & {\it RM3} & 0.2061$^{\uparrow\Uparrow *}$ & 0.3082$^{\uparrow\Uparrow}$ \\ \hline
\end{tabular}
\caption{$\uparrow$ is statistical improvement over query likelihood baseline, $\Uparrow$ is statistical improvement over cross-validated RM3 baseline. An asterisk indicates that the run outperforms its non-RM3 variant with statistical significance.}
\label{table.performance}
\end{table}
